%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% -*- Mode: Latex -*- %%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% uhtest-abstract.tex -- 
%% Author          : Robert Brewer
%% Created On      : Fri Oct  2 16:30:18 1998
%% Last Modified By: Robert Brewer
%% Last Modified On: Fri Oct  2 16:30:25 1998
%% RCS: $Id: uhtest-abstract.tex,v 1.1 1998/10/06 02:06:30 rbrewer Exp $
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%   Copyright (C) 1998 Robert Brewer
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% 

\begin{abstract}
The face of power distribution has changed rapidly over the last several decades.
Modern grids had to adapt to the distributed power generation, and  highly variable loads.
Furthermore as the devices we use every day become more electronically complex,
they become increasingly more sensitive to power quality problems. A distributed 
power quality monitoring systems have been shown to provide real-time insight on the
status of the power grid and even pinpoint the origin of the power disturbance.
Island of Oahu presents a fantastic test bed for such a system. The small power grid
combined with high penetration of distributed renewable energy generators create perfect
conditions for a grid study. Over the last three months we have been collecting power
quality data from several locations of the island as a pilot study for a larger deployment.
This papers describes our methodology, hardware design and presents a preliminary analysis
of the data we collected so far. Lastly this paper lays out the plan for the next
iteration of deployment.
\end{abstract}
